---
title: "DataIO"
output: html_document
---

# Reader (Requirements)
Write your own reader
Requirements:
1. Read line by line
2. Skip potential first n rows
3. Ignore commented rows with '#'
4. Allow several delimiter: white space, tab, comma, semicolon

# Writer (Requirements)
Same as reader only for writing, but allow following two functionalities:
Allow user to write a comment within the file of interes, which is displayed
before everything else in the file. All comments are denoted with '#'
Always include one line after the comment, which is also denoted with '#', which
states the number of lines (with values!) written to the file. This should
count the number of data rows saved in this particular file.

# Task:
Read iris
Create statistical summary: mean and median for all variables, which values are
saved as comment in the output file.


```{r}
my_csv_reader = function(FileName, Path, Separator = ";", SkipRows = 0){
  CSV = NULL
  
  # open
  # substr
  # nchar, length, dim
  # gsub
  # Hint: Concept of "regular expressions"
  #       => search pattern of letters, numbers or special characters within String
  
  # TODO: replace comments with functions, if-conditions, etcpp
  # See for yourself, what type of variables you are getting and working with!
  
  # Prepare datastructure for saving the content of the file => rbind
  # (we are going to read rows and to append rows one after anotjer)
  
  # open connection
  # If skiprows larger 0, then skip some rows before going in to the read mode
  
  while(TRUE){
    # readLines => save function call in variable
    # TODO for yourself: check what datastructure is given in readLines
    # check if there are still lines to read => if-condition
    # Process the line so that you get a vector, where each entry is one word. Avoid a vector of length 1 with one sentence as entry
    # Remember to split the line according to the given separator
    # substr? gsub?
    # Save in data structure
  }
  
  # close connection
  # return your data structure
  return(CSV)
}

```


```{r}
my_csv_writer = function(Data, FileName, Path, Separator = ";", Comments = ""){
  # Get dimensions of Data
  # For-loop through Data by its given rows => dim(Data)[1]
  # NumRows = ???
  
  # open connection
  # writeLines: write your comment before everything else
  for(i in 1:NumRows){
    # writeLines: consider correct separator
  }
  
  # close connection
  
  # Remember: Nothing needs to be returned here!
  # You can create a message with "print()" to notify user about success
}

```





```{r}
# Read

# Statistics
# mean, median, sum, length, nrow, ncol
# 

# Write


```


