---
title: "DataIO"
output: html_document
---

Read iris
Write your own reader
Requirements:
1. Read line by line
2. Skip potential first n rows
3. Ignore commented rows with '#'
4. Allow several delimiter: white space, tab, comma, semicolon

Writer
Same as reader only for writing, but allow following two functionalities:
Allow user to write a comment within the file of interes, which is displayed
before everything else in the file. All comments are denoted with '#'
Always include one line after the comment, which is also denoted with '#', which
states the number of lines (with values!) written to the file. This should
count the number of data rows saved in this particular file.

Task:
Read iris
Create statistical summary: mean and median for all variables, which values are
saved as comment in the output file.


```{r}
my_csv_reader = function(){
  CSV = NULL
  
  # TODO
  
  return(CSV)
}

```


```{r}
my_csv_writer = function(){
  CSV = NULL
  
  # TODO
  
  return(CSV)
}

```







